### 2014-04-05 doc/uist14/disambiguation.tex
adding system and disambiguation, the texts are badly written now, just outlining

This section discusses the three different disambiguation techniques we have proposed.

@@

\subsection{Using Glass Sensors}
\label{sec:using-glass-sensors}

@@

>>>>

For area selection technique, when multiple targets are within the range, the disambiguation is necessary. We propose three different ways of disambiguation solutions in this section. Initially our system leaves the disambiguation to the user \ben{cite our paper}. However, our studies showed that manual disambiguation is a time-consuming task, so we only consult manual action when the system cannot figure out itself. The automatic disambiguation are based on the observation that users tend to adjust their head orientation a bit when they found the target is wrong. So we achieve a more fine-grained targeting by exploiting the IR intensity and the change of IR readings, as well as the sensors on Google Glass.

@@

From the IR datasheet\footnote{https://www.sparkfun.com/datasheets/Components/LED/YSL-R531FR2C-F1.pdf}, for a directional IR emitter, the illuminance at the receiver falls off as the receiver is positioned at an angle from the emitter. Therefore, given multiple targets that are equidistant from the user, the one straight most directly in the line of sight will read the highest intensity values. However, illuminance could also drop off as $\frac{1}{d^2}$ where $d$ is the distance between emitter and receiver. So a closer targets will read higher intensity values. This introduces problems for two targets which are not equidistant from the user, since the closer one will always read a higher value. To overcome this problem, we utilize the fact that the user might move his head a little bit and the changes in the intensity readings will give us such information. We put a higher weight on those with a higher intensity reading gains.

\subsection{Using Glass Sensors}
\label{sec:using-glass-sensors}
The second disambiguation technique is to use the sensors on Google Glass. As we discussed before, Google Glass not only provides us with the head-up display, but also many other sensors. For head orientation, we uses the rotation vector sensor provided by Android API. Such orientation provides the relative movement of user's head. However, without the absolute map, we cannot easily map the readings into targets. In this case, the combination of IR directions provide an anchor direction and the Glass application calibrates its estimation of orientation. From a successful targeting event, we construct the adjacent map during the learning phase and use the model to predict user's targeting if we detect multiple IR readings and also user's head movement.

@@

For cases where the ambient IR noise is too high, and the environment is too dense, or when our disambiguation fails, we always enable the manual disambiguation option to the users. This is achieved in a way similar to mouse click. When the user single click, we only display the current highlighted targets, when the user click again (a double clicke event), we confirm the selection. Therefore, before the second click even happens, the user is always free to change the target by swiping forward or backward.

### 2014-04-05 doc/uist14/system.tex
adding system and disambiguation, the texts are badly written now, just outlining

\section{System Design and Prototyping}
\label{sec:syst-design-prot}
Given the background study on using head orientation for targeting, we have designed and prototyped a low-cost system to study how it can be used in a real-world scenario. In this section, we will first briefly describe our design considerations and then for each considerations we propose commercial off-the-shelf (COTS) solutions that enable our prototyping.

@@

{\bf Adjustable angle:} We learned from the study about human's head orientation pointing that there is a certain bias and variance per person. To fit each person's line of sight, the system should enable adjustability for calibration.

@@

\subsection{IR as beam cursor}
\label{sec:ir-as-beam}

\subsection{Head-up Display}
\label{sec:head-up-display}

\subsection{Wireless Communication}
\label{sec:wirel-comm}

\subsection{3D Printed Adjustable Holder}
\label{sec:3d-print-adjust}

>>>>

\section{System Design and Prototyping}
\label{sec:syst-design-prot}

\ben{This section is still far from my expectation, will refine a lot later! Now I am just laying down ideas.}

Given the background study on using head orientation for targeting, we have designed and prototyped a low-cost system to study how it can be used in a real-world scenario. In this section, we will first briefly describe our design considerations and then for each considerations we propose commercial off-the-shelf (COTS) solutions that enable our prototyping.

@@

{\bf Adjustable angle:} We learned from the study about human's head orientation pointing that there is a certain bias and variance per person. To fit each person's line of sight, the system should enable adjust-ability for calibration.

@@

\subsection{IR as beam cursor}
\label{sec:ir-as-beam}
\ben{will expand on each.}
We choose IR as the proper hardware for the area selection beam for a couple of reasons. First, IR has been used in many home appliances for remote control. Both the emitter and receivers are fairly cheap to manufacture and integrated into devices which can be put in physical environment. Second, the signal characteristics of IR gives us a cone-shape coverage, which is ideal for area selection. While the intensity of IR signal can be easily read from a receiver, it also provides potentials for disambiguation when multiple devices fall in the reception area. Third, IR could be immune to most interference. The ambient could be annoying, but with a combination of IR signal validation, it's still safe. For multipath and reflection exist, the intensity reading can rule out them easily.

Therefore, we can add IR emitter to the user and IR receiver in the environment to detect both IR signals and also the intensity of IR. For the visual feedback from the environment, we designed the system such that when they receive the IR signal and the intensity reading is the largest amongst the nodes that have received an valid signal, it lights up a LED for the beam cursor indication.

\subsection{Head-up Display with interaction capability}
\label{sec:head-up-display}
As we argued for a rich interface, the head-up display (HUD) is an ideal solution to overlay content on top of the physical environment. We have considered a few COTS solutions (including a custom hardware solution, Goggle, Google Glass). And Google Glass has become our choice because it's desigend for everyday use, capable for a rich set of gesture and voice commands, and the head-up display is easy to use and program.

\subsection{Wireless Communication}
\label{sec:wirel-comm}
The IR can be only used for expressing the user's targeting intention, we need another data communication technique that is more reliable and flexible. This is not only necessary for our targeting experiement to transmit received IR signals and the IR intensity readings, but also useful for application development that can exchange arbitrary application-specific messages. We have considered WiFi, Bluetooth Low Energy (BLE) and 802.15.4 (ZigBee) radio. A detailed comparison is out of the scope of this paper, but we have chosen to use 802.15.4 radio, since it is designed for personal area network (PAN) communication, and there are both industrial activity to promote it \footnote{XBee: http://www.digi.com/xbee/} and academia research \cite{watteyne2012openwsn} to make it lower power and more suitable for IoT.

\subsection{3D Printed Adjustable Holder}
\label{sec:3d-print-adjust}
Since we have chosen to use IR for targeting, the holder where IR emitter resides can be designed for adjustment. We have designed a ball-joint model and 3D printed it. See Figure 1.

\subsection{Overall System}
\label{sec:overall-system}
So far, we have described our choice separately, in this subsection we focus on our system architecture that stitches the components together. 
Figure 2 is our overall architecture photo. Because we need to take command from Google Glass, we have used another microcontroller that speaks Bluetooth to communicate with the Google Glass.

%% show the figure here
